\setenumerate{leftmargin=17pt, labelindent=0pt, itemindent=0pt, topsep=0pt, noitemsep}

\begin{singlespace}
 \begin{longtable}[c]{| p{3cm} | p{5.5cm} | p{3cm} | p{3cm} |}
  \hline
  %  \multicolumn{4}{|c|}{Begin of Table}\\
  %
  %  \hline

  Paper & MRs used & Algorithms/Test Cases & Result of MT \\
  \hline
  \endfirsthead
  \hline
  \multicolumn{4}{|c|}{Continuation of Table \ref{long}}                                                                       \\
  \hline
  Paper & MRs used & Algorithms/Test Cases & Result of MT \\
  \hline
  \endhead

  Application of Metamorphic Testing to Supervised Classifiers               &
  MRs for classification algorithms:
  \begin{enumerate}
   % \begin{itemize}[leftmargin=10pt, labelindent=0pt, itemindent=0pt, itemsep=0em]
   \item Consistency with affine transformation.
   \item Permutation of class labels.
   \item Permutation of attributes.
   \item Addition of uninformative/informative attributes.
   \item Consistency with re-prediction.
   \item Addition of training samples.
   \item Addition of classes by duplicating/re-labeling samples.
   \item Removal of classes/samples.
         % \end{itemize}
  \end{enumerate}                                                                           &
  Package: Weka.\par
  \medskip
  Test Case: Randomly generated training and test data. The randomly generated data model does not encapsulate any domain knowledge.                                                             &
  Only a subset of MRs were a necessary property of the corresponding algorithm.\par\medskip
  Several MRs violated NBC algorithms.\par\medskip
  In the case of kNN algorithm, none of the necessary MRs were violated.
  \\

  \hline

  Dataset Coverage for Testing Machine Learning Computer Programs            &
  MR for Pseudo Oracles:
  \begin{enumerate}
   \item Reorder Data Points
   \item Reverse Labels
   \item Reorder Attributes
   \item Add a Constant Attribute
   \item Change Attribute Values
  \end{enumerate}
  \smallskip
  MR for Dataset Generation:
  \begin{enumerate}
   \item Reduce Margin
   \item Insert Noise
   \item Insert Separable
   \item Inconsistent Labels
  \end{enumerate}                                                  &
  Developed a Java program of an SVM classifier\par\medskip
  LIBSVM, used as a pseudo oracle.\par\medskip
  Test Case: Java pseudo random number generator.                            &
  The Java program passed the tests in terms of this criteria. \par\medskip
  When the model constructor component was tested it had some faults that the proposed method identifies.                      \\

  \hline

  Properties of Machine Learning Applications for Use in Metamorphic Testing &
  MartiRank:
  \begin{enumerate}
   \item Additive
   \item Multiplicative
   \item Permutative
   \item Invertive
   \item Inclusive
   \item Exclusive
   \item SVM-Light:
   \item Exclusive
   \item Inclusive
   \item Permutative
  \end{enumerate}
  \par\medskip
  PAYL:
  \begin{enumerate}
   \item Additive
   \item Multiplicative
   \item Permutative
   \item Invertive
   \item Inclusive
   \item Exclusive
  \end{enumerate}                                                  &
  Packages: MartiRank, SVM-Light, PAYL.                                      &
  MartiRank: the implementation produced inconsistent results when a negative label existed.\par\medskip
  SVM-Light not tested because it is inefficient to run the quadratic optimization algorithm on the full data set.\par\medskip
  PAYL exhibits the same six metamorphic properties as MartiRank.                                                              \\

  \hline

  \caption{Synthesis Matrix.\label{long}}
 \end{longtable}

 \begin{longtable}[c]{| p{3cm} | p{4cm} | p{3.5cm} | p{4cm} |}
  \hline
  %  \multicolumn{4}{|c|}{Begin of Table}\\
  %
  %  \hline

  Paper & Domain and Algo tested  & MRs investigated & New Innovative \\
  \hline
  \endfirsthead
  \hline
  \multicolumn{4}{|c|}{Continuation of Table \ref{long}}                                                                       \\
  \hline
  Paper & Domain and Algo tested  & MRs investigated & New Innovative \\
  \hline
  \endhead
  \caption{Synthesis Matrix.\label{long}}
  \endfoot

  Semi-Proving: An Integrated Method for Program Proving, Testing, and Debugging             &
  “Siemens suite of programs” specifically “replace program”: performs regular expression matching and substitutions.                                                                           &
  Given the text 'ab', replacing 'a' with 'x' is equivalent to replacing non-'b' with 'x'. \par\medskip
  'char' and '[char]' are equivalent with the exception of a few wildcards. \par\medskip
  Regular expressions that involve square brackets are equivalent. \par\medskip
  Use '?*' to match the entire input string.                                                             &
  Proof of concept. \par\medskip
  Supports automatic debugging through the identification of constraints for failure-causing inputs.
  \\

  \hline

  Metamorphic Testing Integer Overflow Faults of Mission Critical Program: A Case Study             &
  Integer Overflow Faults in TCAS: tcas.c                                                                           &
  Additive                                                            &
  Proof of concept. \par\medskip
  Formal definition of MR, original test case, follow-up test case, input relation and output relation. \par\medskip
  TCAS case study for demonstration.
  \\

  \hline
  Metamorphic Testing for Software Quality Assessment: A Study of Search Engines             &
  Search engines:
  \begin{enumerate}
    \item Google search
    \item Baidu
    \item Bing
  \end{enumerate}                                                                        &
  \begin{enumerate}
    \item MPSite
    \item MPTitle
    \item MPReverseJD
    \item SwapJD
    \item Top1Absent
  \end{enumerate}                                                         &
  Validation, verification as well as quality assessment.
  \\

  \hline

  Automatic System Testing of Programs without Test Oracles             &
  Machine learning.
  \begin{enumerate}
    \item SVM: Sequential Minimal Optimization (SMO).
    \item C4.5
    \item MartiRank: Area Under the Curve
  \end{enumerate}                                        &
  \begin{enumerate}
    \item Permute
    \item Multiply
    \item Add
    \item Negate
  \end{enumerate}                                          &
  Heuristic Metamorphic Testing.\par\medskip
  Automated Metamorphic System Testing.  \\

  \hline

  Metamorphic Testing and Beyond             &
  A laplace equation with Dirichlet boundary Conditions: “alternating direction implicit” method                                        &
  Beyond identity relations: Convergence                                          &
  Selecting useful MRs. \par\medskip
  Stronger may not necessarily be better than weaker ones. \par\medskip
  Provides guidelines.  \\

  \hline

  A Metamorphic Testing Approach for Online Testing of Service-Oriented Software Applications             &
  service-oriented calculator: arithmetic operators                                        &
  \begin{enumerate}
    \item Commutative
    \item Associative
  \end{enumerate}                                         &
  Methodological steps for online and offline testing. \par\medskip
  MT for service oriented applications.  \\

  \hline

 \end{longtable}
\end{singlespace}
